Data Specialization for a Staged Lambda Calculus

### 2014-11-10 paper/semantics.tex
fold the type validity figure into the syntax figure
more minor fixes

The type validity judgment $\Delta \vdash A \istypewor$, defined in
\cref{fig:validTypes}, ensures that a type $A$ exists at stage $w$; for
example, any type $\fut A$ only exists at stage \bbone.  The typing judgment
$\typeswor e A$ says that $e$ has type $A$ at stage $w$, in the context
$\Gamma$, and is defined in \cref{fig:statics}.  As one would expect, the
typing judgment only produces valid types.
%(by induction on the derivation of the typing judgment).
% under the assumptions in $\Delta$. This context is only augmented by recursive types.

@@

The relation 1-evaluation, defined by $\redonesym$ judgment as shown
in \ref{fig:diaSemantics}, takes an stage \bbone\ term%
\footnote{ The input to $\redonesym$ may be open on stage \bbtwo\ variables, but
the type system ensures that those must occur under a $\next$. Consequently
$\redonesym$ will never directly encounter a variable.}
%
to a residual table $\xi$ and a partial value $v$.  For non-staging
features of \lang, $\redonesym$ is essentially standard call-by-value
evaluation but in addition gathers the subterms' residual tables into
a single table. \ur{The syntax of residual tables should be defined in
  the terminology figure} Residual table entries are created by the
evaluation of \next: 1-evaluation reduces a \next expression by
reducing the body of the \next with 2-evaluation to obtain a
residual $q$ and returns a residual table that maps a freshly
generated variable to the residual.

The relation 2-evaluation, defined by $\redtwosym$ judgment, as shows
in \ref{fig:diaSemantics}, takes a stage \bbtwo\ term and reduces it to
a residual.  Apart from the evaluation of \prev\ and \pause, the
evaluation is straightforward. To reduce a \prev term, 2-evaluation
reduces the body by 1-evaluation to obtain a residual table and a
partial value.  It then reifies the residual table and the partial
value into an residual term, by creating for each variable-residual
pair in the table a corresponding variable binding in the residual,
finally ending with the partial value.

>>>>

\crem{Cut references to type validity.}
The type validity judgment $\Delta \vdash A \istypewor$, defined in
\cref{fig:validTypes}, ensures that a type $A$ exists at stage $w$; for
example, any type $\fut A$ only exists at stage \bbone.  The typing judgment
$\typeswor e A$ says that $e$ has type $A$ at stage $w$, in the context
$\Gamma$, and is defined in \cref{fig:statics}.  As one would expect, the
typing judgment only produces valid types.
%(by induction on the derivation of the typing judgment).
% under the assumptions in $\Delta$. This context is only augmented by recursive types.

@@

The relation 1-evaluation, defined by $\redonesym$ judgment as shown
in \ref{fig:diaSemantics}, takes an stage \bbone\ term%
\footnote{ The input to $\redonesym$ may be open on stage \bbtwo\ variables, but
the type system ensures that those must occur under a $\next$. Consequently
$\redonesym$ will never directly encounter a variable.}
%
to a residual table $\xi$ and a partial value $v$.  For non-staging
features of \lang, $\redonesym$ is essentially standard call-by-value
evaluation but in addition gathers the subterms' residual tables into
a single table. \ur{The syntax of residual tables should be defined in
  the terminology figure} Residual table entries are created by the
evaluation of \next: 1-evaluation reduces a \next\ expression by
reducing the body of the \next\ with 2-evaluation to obtain a
residual $q$ and returns a residual table that maps a freshly
generated variable to the residual.

The relation 2-evaluation, defined by $\redtwosym$ judgment, as shows
in \ref{fig:diaSemantics}, takes a stage \bbtwo\ term and reduces it to
a residual.  Apart from the evaluation of \prev\ and \pause, the
evaluation is straightforward. To reduce a \prev\ term, 2-evaluation
reduces the body by 1-evaluation to obtain a residual table and a
partial value.  It then reifies the residual table and the partial
value into an residual term, by creating for each variable-residual
pair in the table a corresponding variable binding in the residual,
finally ending with the partial value.
